Modalities for Virtualizing Memory Addresses

### 2022-09-28 examples.tex
fix register typo

;; Ensure there's a place to put the L1 mapping
mov %rdi, %r13
call ensure_L1_page
;; Returns the virtual address of the L1 entry in rax
mov %r14, %rax ;; Save that before another call
call alloc_phys_page_or_panic
;; Calculate new PTE by setting the low-order bits
;; of the physical page
add %rax, 3
;; update the page table entry, mapping the page
mov (%rcx), %rax
;; memset the newly-mapped page
mov %rdi, %r13
mov %rsi, 0
mov %rdx, 4096
call memset
;; The newly mapped page is full of 0s
\end{lstlisting}
\caption{Distilled code for mapping a new page}
\label{fig:mapping_code}
\todo[inline]{this is terribly ugly, should switch to minted}
\end{figure}

>>>>

;; Ensure there's a place to put the L1 mapping
mov %rdi, %r13
call ensure_L1_page
;; Returns the virtual address of the L1 entry in rax
mov %r14, %rax ;; Save that before another call
call alloc_phys_page_or_panic
;; Calculate new PTE by setting the low-order bits
;; of the physical page
add %rax, 3
;; update the page table entry, mapping the page
mov (%r14), %rax
;; memset the newly-mapped page
mov %rdi, %r13
mov %rsi, 0
mov %rdx, 4096
call memset
;; The newly mapped page is full of 0s
\end{lstlisting}
\caption{Distilled code for mapping a new page}
\label{fig:mapping_code}
\todo[inline]{this is terribly ugly, should switch to minted}
\end{figure}
